Climate Prediction Markets and Convergence of Predictive Models

### 2015-06-11 prediction_market.Rnw
added the goel et al (2010) prediction without markets idea/cite

From a public policy perspective, changing explanatory models is crucial. Effective climate policy not only requires an accurate consensus on future climate \emph{outcomes}. It also requires an accurate consensus on the causal \emph{mechanisms} influencing such outcomes. If people agree that temperature will rise, but some believe it will be due to greenhouse gases, while others believe that it will be caused by increased solar activity, inconsistent and ineffective policies may be implemented. Our model is designed to investigate whether, and under what conditions, prediction markets can foster such convergence in predictive models.

>>>>

From a public policy perspective, changing the explanatory models of market participants is one of the most important roles that prediction markets might play.\footnote{and perhaps the most important potential social benefit of prediction markets given the comparable predictive power of statistical models, which are less expensive than setting up and maintaining prediction markets \cite{goel_prediction_2010}.} Effective climate policy not only requires an accurate consensus on future climate \emph{outcomes}. It also requires an accurate consensus on the causal \emph{mechanisms} influencing such outcomes. If people agree that temperature will rise, but some believe it will be due to greenhouse gases, while others believe that it will be caused by increased solar activity, inconsistent and ineffective policies may be implemented. Our model is designed to investigate whether, and under what conditions, prediction markets can foster such convergence in predictive models.
